Automating Verification of MPC Security: $\metaprot$ to $\minifed$

### 2023-07-11 popl24/intro.tex
add related work for PPLs

>>>>

Our work also shares many ideas with probabilistic programming
languages designed to perform (exact or approximate)
inference~\cite{holtzen2020scaling, carpenter2017stan, wood2014new,
  bingham2019pyro, albarghouthi2017fairsquare, de2007problog,
  pfeffer2009figaro, saad2021sppl}. Our setting, however, requires
verifying properties beyond inference, including conditional
independence. Recent work by Li et al.~\cite{li2023lilac} proposes a
manual approach for proving such properties, but does not provide
automation.
